---
title: "Five Year Edamame Analysis"
author: Beth M. Duckles, Ph.D. Insightful, LLC 
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Five Year Demographic Data 

```{r data_in, include=FALSE}
source("AnalysisFiveYear/DataReadin_FY.R")
```

### Academic Status 

```{r AcadStatus, echo=FALSE, message=FALSE}

m <- ggplot2::ggplot(data=subset(FYDat,!is.na(AcadStatus)),
            aes(x = AcadStatus))

m + geom_dotplot(dotsize = .7, binwidth = .09, stackratio = 1.1, show.legend = NA) + 
  coord_flip() + 
  labs(x = "Academic Status", y = element_blank()) +
  ggtitle("Academic Status of EDAMAME Attendees 2014-2018") + 
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x=element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  facet_grid(. ~ Year)

```

### Academic Status Table 
```{r AcadSt_PctTable, echo=FALSE, message=FALSE}
# Chart of counts 
t <- FYDat %>% 
  count(AcadStatus, Year) %>% 
  spread(key = Year, value = n) %>% 
  filter(AcadStatus != (is.na(AcadStatus)))

#Change to names so that i can call the years since they're numbers otherwise
names(t) <- c("Ac_Status", "Y2014", "Y2015", "Y2016", "Y2017", "Y2018")

#Arrange in descending order
t <- t %>%   
  arrange(desc(Y2018))

#Change NA's to Zero
t[is.na(t)] <- 0
  
# Chart to Percent and rounding. 
u <- t %>% 
  transmute(Ac_Status, 
    Y2014_pct = Y2014/sum(Y2014)*100, 
    Y2015_pct = Y2015/sum(Y2015)*100,
    Y2016_pct = Y2016/sum(Y2016)*100,
    Y2017_pct = Y2017/sum(Y2017)*100,
    Y2018_pct = Y2018/sum(Y2018)*100)
u <- u %>% 
  mutate(
    Y2014_pct = round(Y2014_pct, digits = 1), 
    Y2015_pct = round(Y2015_pct, digits = 1),
    Y2016_pct = round(Y2016_pct, digits = 1),
    Y2017_pct = round(Y2017_pct, digits = 1),
    Y2018_pct = round(Y2018_pct, digits = 1))

#Rename for the final Table
names(u) <- c("Academic Status", "2014", "2015", "2016", "2017", "2018")

#Make Table 
kable(u) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", full_width = F)) %>% 
  kableExtra::add_header_above(c(" ", "Percent" = 5))
```

There were `r nrow(FYDat)` total respondents to the survey across five years. Yearly totals are as follows: 2014 had `r nrow(d14)`, in 2015 there were `r nrow(d15)` respondents, 2016, there were `r nrow(d16)` respondents, in 2017 there were `r nrow(d17)` respondents and in 2018, there were `r nrow(d18)`. 

### Age 
```{r age, echo=FALSE, message=FALSE}
q <- ggplot(data = subset(FYDat, !is.na(Age)), 
            aes(x = Age)) 

q + geom_dotplot(dotsize = .8, show.legend = NA, na.rm = TRUE) + 
  scale_y_continuous(NULL, breaks = NULL) +
  coord_fixed(ratio = 10) +
  ggtitle("Distribution of EDAMAME Attendee Age 2014-2018") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_grid(Year ~ .)
``` 

### Age Mean/SD 
```{r Age_DescriptTable, echo=FALSE, message=FALSE}
# Chart of median/Avg and sd  
j <- FYDat %>% 
  select(Age, Year) %>%
  na.omit %>% 
  group_by(Year) %>% 
  summarise(
    median = median(Age), 
    average = mean(Age), 
    st_dev = sd(Age))

j <- j %>% 
  mutate(
    average = round(average, digits = 1), 
    st_dev = round(st_dev, digits = 1))

names(j) <- c("Year", "Median", "Average", "St. Dev")
#Make Table 
kable(j) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", full_width = F)) 
```

### Ethnicity 
```{r ethnicity, echo=FALSE, message=FALSE}

n <- ggplot(data = subset(FYDat, !is.na(Ethnicity)), 
            aes(x = Ethnicity))

n + geom_dotplot(dotsize = .6, binwidth = .09, stackratio = 1.1, show.legend = NA) + 
  coord_flip() + 
  labs(x = "Ethnicity", y = element_blank()) +
  ggtitle("Ethnicity of EDAMAME Attendees 2014-2018") + 
  theme(plot.title = element_text(hjust = 0.4), 
        axis.text.x=element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  facet_grid(. ~ Year)

```

### Ethnicity Percentage Table 
```{r Ethnicity_PctTable, echo=FALSE, message=FALSE}
# Chart of counts 
v <- FYDat %>% 
  count(Ethnicity, Year) %>% 
  spread(key = Year, value = n) %>% 
  filter(Ethnicity != (is.na(Ethnicity)))

#Change to names so that i can call the years since they're numbers otherwise
names(v) <- c("Ethn", "Y2014", "Y2015", "Y2016", "Y2017", "Y2018")

#Arrange in descending order
v <- v %>%   
  arrange(desc(Y2018))

#Change NA's to Zero
v[is.na(v)] <- 0
  
# Chart to Percent 
w <- v %>% 
  transmute(Ethn, 
    Y2014_pct = Y2014/sum(Y2014)*100, 
    Y2015_pct = Y2015/sum(Y2015)*100,
    Y2016_pct = Y2016/sum(Y2016)*100,
    Y2017_pct = Y2017/sum(Y2017)*100,
    Y2018_pct = Y2018/sum(Y2018)*100)
w <- w %>% 
  mutate(
    Y2014_pct = round(Y2014_pct, digits = 1), 
    Y2015_pct = round(Y2015_pct, digits = 1),
    Y2016_pct = round(Y2016_pct, digits = 1),
    Y2017_pct = round(Y2017_pct, digits = 1),
    Y2018_pct = round(Y2018_pct, digits = 1))

#Rename for the final Table
names(w) <- c("Ethnicity", "2014", "2015", "2016", "2017", "2018")

#Make Table 
kable(w) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", full_width = F)) %>% 
  kableExtra::add_header_above(c(" ", "Percent" = 5))
```


### Gender 
```{r gender, echo=FALSE, message=FALSE}

r <- ggplot(data = subset(FYDat, !is.na(Gender)), 
            aes(x = Gender))

r + geom_dotplot(binwidth = .28, show.legend = NA) + 
  coord_fixed(ratio = 15) +
  coord_flip() + 
  labs(x = "Gender", y = element_blank()) +
  ggtitle("Gender of EDAMAME Attendees 2014-2018") + 
  theme(plot.title = element_text(hjust = 0.4), 
        axis.text.x=element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  facet_grid (Year ~ .)

```

### Gender Percentage Table 
```{r Gender_PctTable, echo=FALSE, message=FALSE}
# Chart of counts 
g <- FYDat %>% 
  count(Gender, Year) %>% 
  spread(key = Year, value = n) %>% 
  filter(Gender != (is.na(Gender)))

#Change to names so that i can call the years since they're numbers otherwise
names(g) <- c("Gender", "Y2014", "Y2015", "Y2016", "Y2017", "Y2018")

#Arrange in descending order
g <- g %>%   
  arrange(desc(Y2018))

#Change NA's to Zero
g[is.na(g)] <- 0
  
# Chart to Percent 
h <- g %>% 
  transmute(Gender, 
    Y2014_pct = Y2014/sum(Y2014)*100, 
    Y2015_pct = Y2015/sum(Y2015)*100,
    Y2016_pct = Y2016/sum(Y2016)*100,
    Y2017_pct = Y2017/sum(Y2017)*100,
    Y2018_pct = Y2018/sum(Y2018)*100)
h <- h %>% 
  mutate(
    Y2014_pct = round(Y2014_pct, digits = 1), 
    Y2015_pct = round(Y2015_pct, digits = 1),
    Y2016_pct = round(Y2016_pct, digits = 1),
    Y2017_pct = round(Y2017_pct, digits = 1),
    Y2018_pct = round(Y2018_pct, digits = 1))

#Rename for the final Table
names(h) <- c("Gender", "2014", "2015", "2016", "2017", "2018")

#Make Table 
kable(h) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", full_width = F)) %>% 
  kableExtra::add_header_above(c(" ", "Percent" = 5))
```
